---
title: "Scraping Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(usethis)
```

```{r}
use_git_config(user.name = "RoanFM", user.email = "roan.floermartinez522@gmail.com")
```
```{r}
library(tidyverse)
library(rvest) 
library(robotstxt) 
library(formattable)
```

Exercise 1.1 Find the correct selectors for the following fields. Make sure that each matches 762 results:

Course Number
Course Name
Day
Time
Room
Instructor
Avail. / Max
General Education Requirements (make sure you only match 762; beware of the Mac copyright banner at the bottom of the page!)
Description Then, put all this information into one data frame. Do not include any extraneous information like “Instructor:”.

```{r}
fall2017 <- read_html("https://www.macalester.edu/registrar/schedules/2017fall/class-schedule/#crs10008")


course_nums <- 
  fall2017 %>%
  html_nodes(".class-schedule-course-number") %>%
  html_text()

course_names <- 
  fall2017 %>%
  html_nodes(".class-schedule-course-title") %>%
  html_text()

course_days <- fall2017 %>%
  html_nodes("td.class-schedule-label:nth-child(3)") %>% 
  html_text() %>% 
  str_sub(start = 7)
  
course_time <- fall2017 %>% 
  html_nodes("td.class-schedule-label:nth-child(4)") %>%
  html_text() %>% 
  str_sub(start = 7)
  
course_room <- fall2017 %>% 
  html_nodes("td.class-schedule-label:nth-child(5)") %>%
  html_text() %>% 
  str_sub(start = 7)
  
course_instructor <- fall2017 %>% 
  html_nodes("td.class-schedule-label:nth-child(6)") %>%
  html_text() %>% 
  str_sub(start = 13)

course_av <- fall2017 %>% 
  html_nodes("td.class-schedule-label:nth-child(7)") %>%
  html_text() %>% 
  str_sub(start = 14)

course_ger <- fall2017 %>% 
  html_nodes("div.expandable p:nth-child(2)") %>%
  html_text() %>% 
  str_sub(start = 61)

  
course_descriptios <- fall2017 %>% 
  html_nodes("div.expandable p:nth-child(1)") %>%
  html_text() %>% 
  str_sub(start = 30)
```
```{r}



course_df <- tibble(number=course_nums, name=course_names, day=course_days, time=course_time, room=course_room, instructor=course_instructor, avil_max=course_av, general_education_requirement=course_ger, description=course_descriptios)

course_df
```

First six rows of the data frame
```{r}
formattable(head(course_df),align =c("c", "c"), list(`Indicator Name` = formatter("span", style =~style(color = "black",font.weight = "bold"))))
```

```{r fig.height=4, fig.width=14}
course <- course_df %>%  
  separate(number, into = c("department", "number", "section")) 

course %>% 
  group_by(department) %>% 
  summarise(n=n()) %>% 
  ggplot(aes(x=department, y=n))+
  geom_col()
```



Exercise 1.3 Analyze the typical length of course names by department. To do so, create a dplyr pipeline that creates a new data table based on your courses data table, with the following changes:

New columns for the length of the title of a course and the length of the description of the course. Hint: str_length.
Remove departments that have fewer than 10 sections of courses. To do so, group by department, then remove observations in groups with fewer than 10 sections (Hint: use filter with n()). Then ungroup the data.
Create a visualization of the differences across groups in lengths of course names or course descriptions. Think carefully about the visualization you should be using!

```{r}
course_analysis <- course %>% 
  mutate(title_len = str_length(name)) %>% 
  group_by(department) %>% 
  filter(n()>=10) %>% 
  ungroup() 

course_analysis%>% 
  ggplot(aes(x=department, y=title_len))+
  geom_boxplot()+
  theme_classic()
```


